Visualizations for the manuscript

### 2022-03-28 metanalysis_visualization/manuscript_Figures.Rmd
counts by site updated by using count_icd_all as input that contains all months for all sites

counts <- patient_count_psy_period_psy_all %>%
  mutate( total_cases = count_no_psy_patients + count_psy_patients) %>%
  select( siteid, time_p, time, month_year, count_psy_patients, total_cases)

@@

#### All together
```{r}
counts_agg <- patient_count_psy_period_psy_all %>%
  group_by( time_p ) %>%
  mutate( psy_cases = sum( count_psy_patients), 
    total_cases = sum(count_no_psy_patients) + sum(count_psy_patients)) %>%
  select( time_p, time, month_year, psy_cases, total_cases)

>>>>

counts <- count_icd_all %>%
  mutate( time = seq_along(time_p),
         month_year = format(time_p, "%m")) %>%
  select( siteid, time_p, time, month_year, count_psy_patients = count_psy, total_cases = count_icd )

@@

#### All together
```{r}
counts_agg <- counts %>%
  group_by( time_p ) %>%
  mutate( psy_cases = sum( count_psy_patients), 
    total_cases = sum(total_cases)) %>%
  select( time_p, time, month_year, psy_cases, total_cases)
